---
title: "patentr"
author: "Kamil Bojanczyk; Yao Yang"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{patentr}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


The package is a data processing and reporting tool of patent data sets for 
patent analysts.

## Data Input and Cleaning
You can read in patent data files from 
publicly available sources and clean the data into a more useful, 
usable format for further analysis. For example, names are standardized,
dates changed into date format, and application numbers split into country
and number data. Data can be read from data exports found on Sumobrain.com, 
lens.org, and potentially other sources if found to be reproducible and free.

## Data (Re)Processing  
The package will also provide tools to allow the munged data 
to be manually edited in an external tool and re-read into the program. 
Such reprocessing may include verifying assignee names, adding category 
labels, scoring patent quality by various user-defined metrics. Currently,
the method is to export the clean data as a .csv file, manually edit the files
in Google Spreadsheets, and then re-read the program back into R for data
exploration, visualization, and reporting. If time permits, a better 
classification method will be attempted. 

## Data Exploration & Visualization
The package will also allow the user to quickly explore patent trends from the
command line. These trends include simple summary functions, graphics, 
and if time permits, a Shiny dashboard to allow the user to manually summarize 
data into tables and simple graphs. Visualizations are also a part of this step,
however, are more applicable to reporting and thus are discussed in the next
section.


## Visualization & Reporting
The package will also allow the user to output a set of pre-defined plots and 
summary information. Plots may include patent count by assignee, number of 
live applications, total patent count by category, and other interesting 
visualizations. Visualizations will utilize the ggplot package to represent 
highly specific plots that convey a story of the patenting strategy and trends 
of companies and industries. Plots will include patent quality over time, 
patents by jurisdiction, and invention diversity by classification. 


## Audience & Purpose

This package design is inspired by one of the author's work with intellectual
property. Current tools available cost thousands of dollars to use and offer 
outdated or not useful charting features. The authors feel it would beneficial 
to the IP community to have the same quality analysis tools available for free. 

The authors are motivated from lens.org, a site that provides basic access to 
patent resources for free, and they are collaborting with the group as part of 
a larger initiative outside the scope of this class project. Most patent 
analysts run out of time and skill before they can properly analyze portfolios.
This project will address that problem by providing deep insights for free.

The package is aimed at patent agents, lawyers, managers, analysts, and 
academics who are working on patents. This may be used in a patent landscape 
analysis, company IP portfolio analysis, or a freedom to operate search. 


A chief intellectual property officer will use this tool to map the landscape 
of her competitors. She will use the reporting feature to quickly see the 
patent areas of concern, and see how many applications she needs to analyze.

A technology transfer office will use this to generate a landscape of a 
technology field. He will ues this to get rough guidelines for who he should 
be targeting to license a university technology.

An academic will use this tool to deeply analyze trends in patents over time.



Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
